---
title: "Activity Eleven - Biostatistics1"
author: "Taehoon Ha"
date: 11/21/2018
output: 
    github_document:
        toc: true
        toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(microbenchmark)
library(ggplot2)
```

### Question 1
Write a function that generates numbers from $Binomial(n, p)$ distribution using `runif()` function. 
+ Hint: $Binomial(n, p)$ random variable can be defined as a sum of n independent $Bernoulli(p)$ random variables.
```{r}
q1 <- function(n, p) {
    random.binomial <- c()
    for (i in 1:n) {
        random.uniform <- runif(n, 0, 1)
        random.bernoulli <- as.numeric(random.uniform < p)
        random.binomial[i] <- sum(random.bernoulli)
    }
    return(random.binomial)
}
```

<br><br>

### Question 2
Compare performance of your function with `rbinom()` using `microbenchmark()` function.
```{r}
microbenchmark(rbinom(n = 100, size = 100, p = 0.25),
               q1(n = 100, p = 0.25),
               times = 100)
```

<br><br>

### Question 3
Suppose we want to simulate data from a linear regression model:

<p align="center">
<img src = 'https://ws1.sinaimg.cn/large/006tNbRwly1fxgcsuhyd6j30jj02faa6.jpg'>
</p>
<br>

Let $\beta_0$=15 and $\beta_1=0.4$ are known coefficients. Generate data ($N=50$) from this models with given coefficients. Fit a linear regression model and plot fitted values vs. residuals using `ggplot()` function. Please do not forget to use `set.seed()` function for reproductibility.
```{r}
set.seed(1)

# using base plot function
x <- runif(50, 0, 100)
y <- 0.4 * x + rnorm(50, 0, 15)
df <- data.frame(x, y)
mod <- lm(y ~ x, data = df)
x_new <- 1:100
pred <- predict(mod, newdata=data.frame(x = x_new))
plot(df)
lines(x_new, pred, lwd = 3, col = 2)

# using ggplot function
ggplot(df, aes(x, y)) +
    geom_point() +
    geom_smooth(method='lm') +
    theme_bw()
```

<br><br>

### Question 4
Box-Muller algorithm: generate $U_1$ and $U_2$ two independent uniform (0, 1) random variables and set:

<p align="center">
<img src = 'https://ws1.sinaimg.cn/large/006tNbRwly1fxgqt6hpblj309i042t8q.jpg'>
</p>
<br>

are two independent normal variables. Write a function that generates normal variates using Box-Muller
algorithm. Compare simulated data from your function with simulated data from `rnorm()` function
using `ggplot()` (histogram?).

```{r}
newrnorm <- function (n) 
    {
        u1 <- runif(n/2, 0, 1)
        u2 <- runif(n/2, 0, 1)
        theta <- 2 * pi * u2
        R <- sqrt(-2 * log10(u1))
        x <- R * cos(theta)
        y <- R * sin(theta)
        vec <- c(x, y)
        vec
}

x <- seq(-2, 2, length.out = 5000)
y1 <- newrnorm(5000) 
y2 <- rnorm(5000)
Y <- data.frame(y1, y2)

ggplot(data=Y, aes(x= y1, fill = "red")) + 
    geom_histogram(alpha = 0.3) + 
    geom_histogram(aes(x= y2, fill = "blue"), alpha = 0.3) +
    labs(x="X", y="Frequency", title = "Comparison between Box-Muller algorithm and Normal distribution ") +
    scale_fill_discrete(name = "Method", labels=c("Box-Muller Algorithm","Normal Distribution")) +
    theme_bw()
```

