---
title: "Assignment Eleven - Biostatistics1"
author: "Taehoon Ha"
date: 11/23/2018
output: 
    github_document:
        toc: true
        toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(microbenchmark)
library(ggplot2)
```

### 1. Create a GitHub repository Lab11

<br><br>

### 2. Submit your code for all problems from **Activity11**.

<br>

#### Question 1
Write a function that generates numbers from $B(n, p)$ distribution using `runif()` function. 

+ Hint: $B(n, p)$ random variable can be defined as a sum of n independent *Bernoulli(p)* random variables.
```{r}
q1 <- function(n, size, p) {
    random.binomial <- c()
    for (i in 1:n) {
        random.uniform <- runif(size, 0, 1)
        random.bernoulli <- as.numeric(random.uniform < p)
        random.binomial[i] <- sum(random.bernoulli)
    }
    return(random.binomial)
}
```

<br>

#### Question 2
Compare performance of your function with `rbinom()` using `microbenchmark()` function.
```{r}
microbenchmark(rbinom(n = 100, size = 100, p = 0.25),
               q1(n = 100, size = 100, p = 0.25),
               times = 100)
```

<br>

#### Question 3
Suppose we want to simulate data from a linear regression model:

<p align="center">
<img src = 'https://ws1.sinaimg.cn/large/006tNbRwly1fxgcsuhyd6j30jj02faa6.jpg'>
</p>
<br>

Let $\beta_0$=15 and $\beta_1=0.4$ are known coefficients. Generate data ($N=50$) from this models with given coefficients. Fit a linear regression model and plot fitted values vs. residuals using `ggplot()` function. Please do not forget to use `set.seed()` function for reproductibility.
```{r}
set.seed(1)

x <- runif(50, 20, 40)
y <- 15 + 0.4 * x + rnorm(50, 0, 3)
data.xy <- data.frame(x, y)
lrm <- lm(y ~ x, data = data.xy)
data.xy$prd <- predict(lrm)
data.xy$res <- residuals(lrm)

# using ggplot function
ggplot(lrm, aes(.fitted, .resid)) + 
    geom_point() + 
    stat_smooth(method = "auto", se = F, col = 'red') + 
    geom_hline(yintercept = 0, linetype = "dashed") + 
    xlab("Fitted values") + 
    ylab("Residuals") + 
    ggtitle("Residual vs Fitted Plot") +
    theme_bw() + 
    theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold"))

ggplot(data.xy, aes(x,y)) +
    geom_smooth(method = "lm", color = 4) +
    geom_segment(aes(xend = x, yend = prd, alpha = 0.3)) +
    geom_point(aes(color = res)) +
    scale_color_gradient2(low = 4, mid = 3, high = 2) +
    geom_point(aes(y = prd), shape = 19, col = 1, lwd = 1) +
    theme_bw()
```

<br>

#### Question 4
Box-Muller algorithm: generate $U_1$ and $U_2$ two independent uniform (0, 1) random variables and set:

<p align="center">
<img src = 'https://ws1.sinaimg.cn/large/006tNbRwly1fxgqt6hpblj309i042t8q.jpg'>
</p>
<br>

are two independent normal variables. Write a function that generates normal variates using Box-Muller
algorithm. Compare simulated data from your function with simulated data from `rnorm()` function using `ggplot()` (histogram?).

```{r}
newrnorm <- function(n) {
    u1 <- runif(n/2, 0, 1)
    u2 <- runif(n/2, 0, 1)
    
    theta <- 2 * pi * u2
    R <- sqrt(-2 * log(u1))
    
    x <- R * cos(theta)
    y <- R * sin(theta)
    
    vec <- c(x, y)
    vec
}

x <- seq(-2, 2, length.out = 5000)
y1 <- newrnorm(5000)
y2 <- rnorm(5000)
Y <- data.frame(y1, y2)

# using ggplot
ggplot(data = Y, aes(x = y1, fill = "red")) +
    geom_histogram(alpha = 0.3) + 
    geom_histogram(aes(x = y2, fill = "blue"), alpha = 0.3) +
    labs(x = "X", 
         y = "Frequency", 
         title = "Comparison between Box-Muller algorithm and Normal distribution") + 
    scale_fill_discrete(name = "Method", 
                        labels = c("Box-Muller Algorithm", "Normal Distribution")) +
    theme_bw()
```

<br><br>

### 3. Please make sure your code is formatted according to the style guide.